Child Signals of Need in Utila, Honduras: An Exploratory Study

### 2024-09-27 Paper.qmd
Updated dictionaries.R and updated paper to use these dictionaries.

```{r setup, include=FALSE}
# source("dictionaries.R")
source("analysisforpaper.R", local = knitr::knit_global()) # experiment with taking this away

@@

kable(custom.summarize(modeldf, vars_c, facvar = "Sex")) %>% kable_styling()

@@

kable(custom.summarize(caregivers, vars_c)) %>% kable_styling()

@@

```{r}
#| label: tbl-main_models
#| tbl-cap: Regression tables for our main exploratory models.
r_vars <- c(
  ChildAge = "Age (years)",
  SexMale = "Sex (male)",
  OtherChildrenHH = "Other children",
  LogIncome = "Income (log)",
  number_adults = "Adults in home",
  PartnerStatusUnpartnered = "Partner status (single)",
  EducationLevelYears = "Parent ed. (years)",
  ConflictFreqN = "Conflict freq.",
  SignalFreq = "Signal freq.",
  SignalCost = "Signal cost",
  SignalFreqMax = "Max signal freq.",
  IllnessSusceptibilityMean = "Percieved illness susceptibility",
  SadFreqN = "Sadness freq.",
  CryFreqN = "Crying freq.",
  TantrumFreqN = "Tantrum freq.",
  AlloparentingFreqN = "Child allocare"
)
modelsummary(list(Sadness = msadH, Crying = mcryH, Tantrum = mtantrumH, SignalFreq = msfH, SignalCost = mscH, SignalFreqMax = mmsfH), gof_map = "nobs", coef_rename = r_vars, stars = c('*' = .05, '**' = .01, '***' = .001), coef_omit = "(Intercept)")
```

@@

```{r}
#| label: tbl-conflict_dep_var
#| tbl-cap: Regression table for the model examining the frequency of conflict between child and caretaker as the dependent variable.
r_vars <- c(
  ChildAge = "Age (years)",
  SexMale = "Sex (male)",
  OtherChildrenHH = "Other children",
  LogIncome = "Income (log)",
  number_adults = "Adults in home",
  PartnerStatusUnpartnered = "Partner status (single)",
  EducationLevelYears = "Parent ed. (years)",
  ConflictFreqN = "Conflict freq.",
  SignalFreq = "Signal freq.",
  SignalCost = "Signal cost",
  SignalFreqMax = "Max signal freq.",
  IllnessSusceptibilityMean = "Percieved illness susceptibility",
  SadFreqN = "Sadness freq.",
  CryFreqN = "Crying freq.",
  TantrumFreqN = "Tantrum freq.",
  AlloparentingFreqN = "Child allocare",
  TricepR = "Tricep skinfold (residuals)",
  SubscapR = "Subscapular skinfold (residuals)",
  BodyFat = "BodyFat (composite)",
  RelativeNeed3 = "Relative need (w/in household)",
  UnwantedTask = "Unwanted task",
  Punishment21 = "Punishment",
  Family21 = "Family conflict",
  DiscomfortPainInjuryIllness = "Discomfort/Pain/Injury/Illness",
  CaregiverResponse = "Caregiver Response",
  OlderKids = "Older children",
  YoungerKids = "Younger children",
  AdultsNoChildcare = "Adults that do not provide childcare",
  AdultsChildcare = "Adults that provide childcare",
  OtherChildAlloparentingFreqN = "Other household child alloparenting freq."
)
modelsummary(mconflict, gof_map = "nobs", coef_rename = r_vars, stars = c('*' = .05, '**' = .01, '***' = .001), coef_omit = "(Intercept)")
```

@@

```{r}
#| label: tbl-alloparenting_dep_var
#| tbl-cap: Regression table for the model examining the frequency of conflict between child and caretaker as the dependent variable.
r_vars <- c(
  ChildAge = "Age (years)",
  SexMale = "Sex (male)",
  OtherChildrenHH = "Other children",
  LogIncome = "Income (log)",
  number_adults = "Adults in home",
  PartnerStatusUnpartnered = "Partner status (single)",
  EducationLevelYears = "Parent ed. (years)",
  ConflictFreqN = "Conflict freq.",
  SignalFreq = "Signal freq.",
  SignalCost = "Signal cost",
  SignalFreqMax = "Max signal freq.",
  IllnessSusceptibilityMean = "Percieved illness susceptibility",
  SadFreqN = "Sadness freq.",
  CryFreqN = "Crying freq.",
  TantrumFreqN = "Tantrum freq.",
  AlloparentingFreqN = "Child allocare",
  TricepR = "Tricep skinfold (residuals)",
  SubscapR = "Subscapular skinfold (residuals)",
  BodyFat = "BodyFat (composite)",
  RelativeNeed3 = "Relative need (w/in household)",
  UnwantedTask = "Unwanted task",
  Punishment21 = "Punishment",
  Family21 = "Family conflict",
  DiscomfortPainInjuryIllness = "Discomfort/Pain/Injury/Illness",
  CaregiverResponse = "Caregiver Response",
  OlderKids = "Older children",
  YoungerKids = "Younger children",
  AdultsNoChildcare = "Adults that do not provide childcare",
  AdultsChildcare = "Adults that provide childcare",
  OtherChildAlloparentingFreqN = "Other household child alloparenting freq."
)
modelsummary(malloparenting, gof_map = "nobs", coef_rename = r_vars, stars = c('*' = .05, '**' = .01, '***' = .001), coef_omit = "(Intercept)")
```

@@

```{r}
#| label: tbl-bodyfat_models
#| tbl-cap: Regression tables for the models examining the effect of body fat on signaling.
r_vars <- c(
  ChildAge = "Age (years)",
  SexMale = "Sex (male)",
  OtherChildrenHH = "Other children",
  LogIncome = "Income (log)",
  number_adults = "Adults in home",
  PartnerStatusUnpartnered = "Partner status (single)",
  EducationLevelYears = "Parent ed. (years)",
  ConflictFreqN = "Conflict freq.",
  SignalFreq = "Signal freq.",
  SignalCost = "Signal cost",
  SignalFreqMax = "Max signal freq.",
  IllnessSusceptibilityMean = "Percieved illness susceptibility",
  SadFreqN = "Sadness freq.",
  CryFreqN = "Crying freq.",
  TantrumFreqN = "Tantrum freq.",
  AlloparentingFreqN = "Child allocare",
  TricepR = "Tricep skinfold (residuals)",
  SubscapR = "Subscapular skinfold (residuals)",
  BodyFat = "BodyFat (composite)"
)
modelsummary(list(Sadness = mBFsad, Crying = mBFcry, Tantrum = mBFtantrum, SignalFreq = mBFf, SignalCost = mBFc, SignalFreqMax = mBFfm), gof_map = "nobs", coef_rename = r_vars, stars = c('*' = .05, '**' = .01, '***' = .001), coef_omit = "(Intercept)")
```

@@

modelsummary(list(Weight2024 = weight_long_cry, Height2024 = height_long_cry), gof_map = "nobs", coef_rename = r_vars, stars = c('*' = .05, '**' = .01, '***' = .001), coef_omit = "(Intercept)")
```

@@

```{r}
#| label: tbl-need_models
#| tbl-cap: Regression tables for the models examining relative perceptions of child need within the family as a dependent variable.
r_vars <- c(
  ChildAge = "Age (years)",
  SexMale = "Sex (male)",
  OtherChildrenHH = "Other children",
  LogIncome = "Income (log)",
  number_adults = "Adults in home",
  PartnerStatusUnpartnered = "Partner status (single)",
  EducationLevelYears = "Parent ed. (years)",
  ConflictFreqN = "Conflict freq.",
  SignalFreq = "Signal freq.",
  SignalCost = "Signal cost",
  SignalFreqMax = "Max signal freq.",
  IllnessSusceptibilityMean = "Percieved illness susceptibility",
  SadFreqN = "Sadness freq.",
  CryFreqN = "Crying freq.",
  TantrumFreqN = "Tantrum freq.",
  AlloparentingFreqN = "Child allocare",
  TricepR = "Tricep skinfold (residuals)",
  SubscapR = "Subscapular skinfold (residuals)",
  BodyFat = "BodyFat (composite)",
  RelativeNeed3 = "Relative need (w/in household)"
)
modelsummary(list(SignalFreq = mN1, SignalCost = mN2), vcov = vcovCL, type = "HC0", cluster = ~householdID, gof_map = "nobs", coef_rename = r_vars, stars = c('*' = .05, '**' = .01, '***' = .001), coef_omit = "(Intercept)")
```

@@

```{r}
#| label: tbl-last_signal_model
#| tbl-cap: Regression table for the model examining responses to the last time a child was sad or cried.
r_vars <- c(
  ChildAge = "Age (years)",
  SexMale = "Sex (male)",
  OtherChildrenHH = "Other children",
  LogIncome = "Income (log)",
  number_adults = "Adults in home",
  PartnerStatusUnpartnered = "Partner status (single)",
  EducationLevelYears = "Parent ed. (years)",
  ConflictFreqN = "Conflict freq.",
  SignalFreq = "Signal freq.",
  SignalCost = "Signal cost",
  SignalFreqMax = "Max signal freq.",
  IllnessSusceptibilityMean = "Percieved illness susceptibility",
  SadFreqN = "Sadness freq.",
  CryFreqN = "Crying freq.",
  TantrumFreqN = "Tantrum freq.",
  AlloparentingFreqN = "Child allocare",
  TricepR = "Tricep skinfold (residuals)",
  SubscapR = "Subscapular skinfold (residuals)",
  BodyFat = "BodyFat (composite)",
  RelativeNeed3 = "Relative need (w/in household)",
  UnwantedTask = "Unwanted task",
  Punishment21 = "Punishment",
  Family21 = "Family conflict",
  DiscomfortPainInjuryIllness = "Discomfort/Pain/Injury/Illness",
  CaregiverResponse = "Caregiver Response"
)
modelsummary(mpr, vcov = vcovCL, type = "HC0", cluster = ~householdID, gof_map = "nobs", coef_rename = r_vars, stars = c('*' = .05, '**' = .01, '***' = .001), coef_omit = "(Intercept)")
```

>>>>

```{r setup, include=FALSE}
source("dictionaries.R", local = knitr::knit_global())
source("analysisforpaper.R", local = knitr::knit_global())

@@

#kable(custom.summarize(modeldf, vars_c, facvar = "Sex")) %>% kable_styling()
kable(custom.summarize(modeldf, longform_dict[1:18])) %>% kable_styling()

@@

kable(custom.summarize(caregivers, longform_dict[19:23])) %>% kable_styling()

@@

```{r}
#| label: tbl-main_models
#| tbl-cap: Regression tables for our main exploratory models.
r_vars <- c(
  ChildAge = "Age (years)",
  SexMale = "Sex (male)",
  OtherChildrenHH = "Other children",
  LogIncome = "Income (log)",
  number_adults = "Adults in home",
  PartnerStatusUnpartnered = "Partner status (single)",
  EducationLevelYears = "Parent ed. (years)",
  ConflictFreqN = "Conflict freq.",
  SignalFreq = "Signal freq.",
  SignalCost = "Signal cost",
  SignalFreqMax = "Max signal freq.",
  IllnessSusceptibilityMean = "Percieved illness susceptibility",
  SadFreqN = "Sadness freq.",
  CryFreqN = "Crying freq.",
  TantrumFreqN = "Tantrum freq.",
  AlloparentingFreqN = "Child allocare"
)
# modelsummary(list(Sadness = msadH, Crying = mcryH, Tantrum = mtantrumH, SignalFreq = msfH, SignalCost = mscH, SignalFreqMax = mmsfH), gof_map = "nobs", coef_rename = r_vars, stars = c('*' = .05, '**' = .01, '***' = .001), coef_omit = "(Intercept)")

modelsummary(list(Sadness = msadH, Crying = mcryH, Tantrum = mtantrumH, SignalFreq = msfH, SignalCost = mscH, SignalFreqMax = mmsfH), gof_map = "nobs", coef_rename = shortform_dict, stars = c('*' = .05, '**' = .01, '***' = .001), coef_omit = "(Intercept)")
```

@@

```{r}
#| label: tbl-conflict_dep_var
#| tbl-cap: Regression table for the model examining the frequency of conflict between child and caretaker as the dependent variable.
r_vars <- c(
  ChildAge = "Age (years)",
  SexMale = "Sex (male)",
  OtherChildrenHH = "Other children",
  LogIncome = "Income (log)",
  number_adults = "Adults in home",
  PartnerStatusUnpartnered = "Partner status (single)",
  EducationLevelYears = "Parent ed. (years)",
  ConflictFreqN = "Conflict freq.",
  SignalFreq = "Signal freq.",
  SignalCost = "Signal cost",
  SignalFreqMax = "Max signal freq.",
  IllnessSusceptibilityMean = "Percieved illness susceptibility",
  SadFreqN = "Sadness freq.",
  CryFreqN = "Crying freq.",
  TantrumFreqN = "Tantrum freq.",
  AlloparentingFreqN = "Child allocare",
  TricepR = "Tricep skinfold (residuals)",
  SubscapR = "Subscapular skinfold (residuals)",
  BodyFat = "BodyFat (composite)",
  RelativeNeed3 = "Relative need (w/in household)",
  UnwantedTask = "Unwanted task",
  Punishment21 = "Punishment",
  Family21 = "Family conflict",
  DiscomfortPainInjuryIllness = "Discomfort/Pain/Injury/Illness",
  CaregiverResponse = "Caregiver Response",
  OlderKids = "Older children",
  YoungerKids = "Younger children",
  AdultsNoChildcare = "Adults that do not provide childcare",
  AdultsChildcare = "Adults that provide childcare",
  OtherChildAlloparentingFreqN = "Other household child alloparenting freq."
)
modelsummary(mconflict, gof_map = "nobs", coef_rename = shortform_dict, stars = c('*' = .05, '**' = .01, '***' = .001), coef_omit = "(Intercept)")
```

@@

```{r}
#| label: tbl-alloparenting_dep_var
#| tbl-cap: Regression table for the model examining the frequency of conflict between child and caretaker as the dependent variable.
r_vars <- c(
  ChildAge = "Age (years)",
  SexMale = "Sex (male)",
  OtherChildrenHH = "Other children",
  LogIncome = "Income (log)",
  number_adults = "Adults in home",
  PartnerStatusUnpartnered = "Partner status (single)",
  EducationLevelYears = "Parent ed. (years)",
  ConflictFreqN = "Conflict freq.",
  SignalFreq = "Signal freq.",
  SignalCost = "Signal cost",
  SignalFreqMax = "Max signal freq.",
  IllnessSusceptibilityMean = "Percieved illness susceptibility",
  SadFreqN = "Sadness freq.",
  CryFreqN = "Crying freq.",
  TantrumFreqN = "Tantrum freq.",
  AlloparentingFreqN = "Child allocare",
  TricepR = "Tricep skinfold (residuals)",
  SubscapR = "Subscapular skinfold (residuals)",
  BodyFat = "BodyFat (composite)",
  RelativeNeed3 = "Relative need (w/in household)",
  UnwantedTask = "Unwanted task",
  Punishment21 = "Punishment",
  Family21 = "Family conflict",
  DiscomfortPainInjuryIllness = "Discomfort/Pain/Injury/Illness",
  CaregiverResponse = "Caregiver Response",
  OlderKids = "Older children",
  YoungerKids = "Younger children",
  AdultsNoChildcare = "Adults that do not provide childcare",
  AdultsChildcare = "Adults that provide childcare",
  OtherChildAlloparentingFreqN = "Other household child alloparenting freq."
)
modelsummary(malloparenting, gof_map = "nobs", coef_rename = shortform_dict, stars = c('*' = .05, '**' = .01, '***' = .001), coef_omit = "(Intercept)")
```

@@

```{r}
#| label: tbl-bodyfat_models
#| tbl-cap: Regression tables for the models examining the effect of body fat on signaling.
r_vars <- c(
  ChildAge = "Age (years)",
  SexMale = "Sex (male)",
  OtherChildrenHH = "Other children",
  LogIncome = "Income (log)",
  number_adults = "Adults in home",
  PartnerStatusUnpartnered = "Partner status (single)",
  EducationLevelYears = "Parent ed. (years)",
  ConflictFreqN = "Conflict freq.",
  SignalFreq = "Signal freq.",
  SignalCost = "Signal cost",
  SignalFreqMax = "Max signal freq.",
  IllnessSusceptibilityMean = "Percieved illness susceptibility",
  SadFreqN = "Sadness freq.",
  CryFreqN = "Crying freq.",
  TantrumFreqN = "Tantrum freq.",
  AlloparentingFreqN = "Child allocare",
  TricepR = "Tricep skinfold (residuals)",
  SubscapR = "Subscapular skinfold (residuals)",
  BodyFat = "BodyFat (composite)"
)
modelsummary(list(Sadness = mBFsad, Crying = mBFcry, Tantrum = mBFtantrum, SignalFreq = mBFf, SignalCost = mBFc, SignalFreqMax = mBFfm), gof_map = "nobs", coef_rename = shortform_dict, stars = c('*' = .05, '**' = .01, '***' = .001), coef_omit = "(Intercept)")
```

@@

modelsummary(list(Weight2024 = weight_long_cry, Height2024 = height_long_cry), gof_map = "nobs", coef_rename = shortform_dict, stars = c('*' = .05, '**' = .01, '***' = .001), coef_omit = "(Intercept)")
```

@@

```{r}
#| label: tbl-need_models
#| tbl-cap: Regression tables for the models examining relative perceptions of child need within the family as a dependent variable.
r_vars <- c(
  ChildAge = "Age (years)",
  SexMale = "Sex (male)",
  OtherChildrenHH = "Other children",
  LogIncome = "Income (log)",
  number_adults = "Adults in home",
  PartnerStatusUnpartnered = "Partner status (single)",
  EducationLevelYears = "Parent ed. (years)",
  ConflictFreqN = "Conflict freq.",
  SignalFreq = "Signal freq.",
  SignalCost = "Signal cost",
  SignalFreqMax = "Max signal freq.",
  IllnessSusceptibilityMean = "Percieved illness susceptibility",
  SadFreqN = "Sadness freq.",
  CryFreqN = "Crying freq.",
  TantrumFreqN = "Tantrum freq.",
  AlloparentingFreqN = "Child allocare",
  TricepR = "Tricep skinfold (residuals)",
  SubscapR = "Subscapular skinfold (residuals)",
  BodyFat = "BodyFat (composite)",
  RelativeNeed3 = "Relative need (w/in household)"
)
modelsummary(list(SignalFreq = mN1, SignalCost = mN2), vcov = vcovCL, type = "HC0", cluster = ~householdID, gof_map = "nobs", coef_rename = shortform_dict, stars = c('*' = .05, '**' = .01, '***' = .001), coef_omit = "(Intercept)")
```

@@

```{r}
#| label: tbl-last_signal_model
#| tbl-cap: Regression table for the model examining responses to the last time a child was sad or cried.
r_vars <- c(
  ChildAge = "Age (years)",
  SexMale = "Sex (male)",
  OtherChildrenHH = "Other children",
  LogIncome = "Income (log)",
  number_adults = "Adults in home",
  PartnerStatusUnpartnered = "Partner status (single)",
  EducationLevelYears = "Parent ed. (years)",
  ConflictFreqN = "Conflict freq.",
  SignalFreq = "Signal freq.",
  SignalCost = "Signal cost",
  SignalFreqMax = "Max signal freq.",
  IllnessSusceptibilityMean = "Percieved illness susceptibility",
  SadFreqN = "Sadness freq.",
  CryFreqN = "Crying freq.",
  TantrumFreqN = "Tantrum freq.",
  AlloparentingFreqN = "Child allocare",
  TricepR = "Tricep skinfold (residuals)",
  SubscapR = "Subscapular skinfold (residuals)",
  BodyFat = "BodyFat (composite)",
  RelativeNeed3 = "Relative need (w/in household)",
  UnwantedTask = "Unwanted task",
  Punishment21 = "Punishment",
  Family21 = "Family conflict",
  DiscomfortPainInjuryIllness = "Discomfort/Pain/Injury/Illness",
  CaregiverResponse = "Caregiver Response"
)
modelsummary(mpr, vcov = vcovCL, type = "HC0", cluster = ~householdID, gof_map = "nobs", coef_rename = shortform_dict, stars = c('*' = .05, '**' = .01, '***' = .001), coef_omit = "(Intercept)")
```
